From Reversible Programs to \\ Univalent Universes and Back

### 2021-10-26 Pi/paper/equivalence.tex
Fix typo on l1025
Fixes #137
Fix the composition symbol

Finally, we show how to interpret $\PiHatLang$ to $\UFin$, and back from $\UFin$ to $\PiHatLang$. Types in $\PiHatLang$
are interpreted as 0-cells in $\UFin$, that is, a natural number $n$ is mapped to $\Fin[n]$. The 1-combinators in
$\PiHatLang$ are mapped to 1-paths in $\UFin$, that is, 1-loops $\Aut[\Fin[n]]$, in each connected component. In
$\PiHatLang$, the 1-combinators are generated by adjacent transpositions, so these can be mapped to words in $\Sn$ and
then to automorphisms using~\Cref{prop:sn-lehmer-fin-equiv}. Finally, 2-combinators are mapped to 2-paths between loops
in $\UFin$.

@@

Recall the specification of reversible disjunction from \Cref{sec:examples}, the two Qiskit circuits for implementing
it, and the corresponding $\PiLang$ definitions \Afun{reversibleOr1} and \Afun{reversibleOr2}. The normal forms for both
circuits compute to the following, establishing their equivalence:

@@

Instead of manually producing $\Pi$-programs to implement the reversible disjunction specification, it is also possible
to simply quote the desired permutation:

>>>>

Finally, we show how to interpret $\PiHatLang$ to $\UFin$, and back from $\UFin$ to $\PiHatLang$. Types in $\PiHatLang$
are interpreted as 0-cells in $\UFin$, that is, a natural number $n$ is mapped to $\Fin[n]$. The 1-combinators in
$\PiHatLang$ are mapped to 1-paths in $\UFin$, that is, 1-loops in each connected component, equivalent to
$\Aut[\Fin[n]]$. In $\PiHatLang$, the 1-combinators are generated by adjacent transpositions, so these can be mapped to
words in $\Sn$ and then to automorphisms using~\Cref{prop:sn-lehmer-fin-equiv}. Finally, 2-combinators are mapped to
2-paths between loops in $\UFin$.

@@

Recall the specification of reversible disjunction from \Cref{sec:examples}, the two Qiskit circuits for implementing
it, and the corresponding $\PiLang$ definitions \Afun{reversibleOr1} and \Afun{reversibleOr2}. The type $\mathbb{B}\ 3$
normalises to $\mathbb{8}+ = \mathbb{1} + (\mathbb{1} + (\mathbb{1} + (\mathbb{1} + (\mathbb{1} + (\mathbb{1} + (\mathbb{1} +
(\mathbb{1} + \mathbb{0})))))))$, and normal forms for both circuits compute to the following, establishing their equivalence:

@@

Instead of manually producing $\Pi$-programs to implement the reversible disjunction specification, it is possible to
simply quote the desired permutation (using a function $\term{lookup}$ to read a tabulated version for readability):
